Simulating dynein's powerstroke using Brownian dynamics

### 2017-05-31 thesis/latex/thesis.tex
Thesis: add column to literature values tbale.

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
    $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm && & 11.15nm & & & \\ \hline
    $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & &2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
    $c_t$ & & && & & & \\ \hline
    $c_m$ & & && & & & \\ \hline
    $c_b$ & & && & 140 kJ/mol & & \\ \hline
  \end{tabular}
  \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
  \label{table:parameter-table}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
  \begin{tabular}{| l | l | l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Leschziner \cite{leschziner} & Kon & Burgess \\\hline
    $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
    $L_t$ &  7nm && & 11.15nm & & & \\ \hline
    $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
    $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
    $R_t$ &  & & &2.16nm & & & \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & 60 & & \\ \hline
    $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
    $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
  \end{tabular}
  \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
  \label{table:parameter-table}
\end{figure}

%% \begin{figure}[h]
%%   \centering
%%   \begin{tabular}{| l | l | l | l | l | l | l | l |}
%%     \hline
%%     & Winch (Sarlah) & Lin & PyMol 3VKH & PyMol 4RH7 & Redwine & Kon & Burgess \\\hline
%%     $L_s$ & 12nm && 21.0nm & 22.1nm & & & \\ \hline
%%     $L_t$ &  7nm && & 11.15nm & & & \\ \hline
%%     $R_b$ &  && 1.57nm & 1.45nm & & & \\ \hline
%%     $R_m$ &  7nm && 7.36nm & 6.3nm & & & \\ \hline
%%     $R_t$ &  & & &2.16nm & & & \\ \hline
%%     $\theta_{m}^{Pre}$ & 250$^{\circ}$ &171$^{\circ}$ & & & & & 160\\ \hline
%%     $\theta_{m}^{Post}$ & 330$^{\circ}$ &137.5$^{\circ}$ & & & & & 136\\ \hline
%%     $\theta_{b}$ & 56$^{\circ}$ &63.5$^{\circ}$ & & & & & \\ \hline
%%     $\theta_{t}$ & 0$^{\circ}$ && & & & & \\ \hline
%%     $k_{ub}$ & $180 s^{-1,a}$ && & & & $90.2 \pm 4.5$& \\ \hline
%%     $k_b$ & $460 s^{-1,b}$ && & & & & \\ \hline
%%     $c_t$ & & && & & & \\ \hline
%%     $c_m$ & & && & & & \\ \hline
%%     $c_b$ & & && & 140 kJ/mol & & \\ \hline
%%   \end{tabular}
%%   \caption{Literature values for dynein model parameters.}{A table of values collected from various literature sources , other simulations and crystal structures.}
%%   \label{table:parameter-table}
%% \end{figure}
